\propertitle

### 2019-04-18 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-04-11T00:12:54+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation constraints%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample constraints}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

%\usepackage{wrapfig}

@@

\hrule
Yasser's intro
\hrule

Experimental technologies to record the activity of many neurons at the
same time in different species and brain areas are rapidly advancing. These
experimental advancements are paralleled by advances in theoretical and
computational methods for analyzing the data accumulated using the
recording technologies. Such theoretical methods usually take the form of
probabilistic models that try to describe the multi-neuronal activity of
the recorded neurons. With such probabilistic models one aims to address
numerous issues: What correlations are important in describing the
multi-neuronal pattern? How does the pattern of activity covary with
external stimuli or experimental conditions? What dimensionality does the
neural data live in and how is this related to the underlying network
interactions? The probabilistic models can also be used to make predictions
about the structure of the neural code, by studying the properties of the
fitted model, or by generating synthetic data from it.

@@

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-04-18T16:17:13+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation constraints%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample constraints}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\usepackage{wrapfig}

@@

A necessary step of every plausible inference is the assignment of some
probabilistic premisses -- as many as necessary to arrive at our desired
probabilistic conclusions given the evidence. The necessity of this step
was tersely stated by W.~E.~Johnson %(J.~M.~Keynes's supervisor)
a hundred years ago:
\begin{quote}\footnotesize
  Now the axioms of probability enable us to infer any
  probability-conclusion \emph{only} from probability-premisses. In other
  words, the calculus of probability does not enable us to infer any
  probability-value unless we have some probabilities or probability
  relations \emph{given}. Such data cannot be supplied by the
  mathematician. E.g. the rules of arithmetic and the axioms of the
  probability-calculus are utterly impotent to determine, on the supposed
  knowledge that the throw of a coin must yield either head or tail and
  cannot yield both, the probability that it will yield head or that it
  will yield tail. We must assume that the two co-exclusive and
  co-exhaustive possibilities are \emph{equally probable}, before we can
  estimate the probability of either as being a half of certitude.
  \sourceatright{\citep[Appendix on eduction, \sect~5,
    p.~182]{johnson1924}}
\end{quote}

These premisses may represent either actual knowledge or just some
hypotheses whose consequences we want to explore. They can be
\setlength{\intextsep}{0.5ex}% with wrapfigure
\begin{wrapfigure}{l}{0.33\linewidth}% with wrapfigure
\centering\includegraphics[width=\linewidth]{statements_scheme1.pdf}%\\
%\caption{caption}\label{fig:comparison_a5}
\end{wrapfigure}% statements_scheme.svg statements_scheme2.svg
assigned at different depths of the logical analysis of our inference
problem, and assignments at different depths can turn out to be
equivalent.

We can for example assign probabilistic premisses at a very deep
level, as schematically illustrated on the left. They will determine the
probabilities of statements at all higher levels, including the statements
we're ultimately interested in.

Or we can assign probabilistic premisses at
a level of intermediate
\begin{wrapfigure}{r}{0.33\linewidth}% with wrapfigure
\centering\includegraphics[width=\linewidth]{statements_scheme2.pdf}%\\
%\caption{caption}\label{fig:comparison_a5}
\end{wrapfigure}% statements_scheme.svg statements_scheme2.svg
depth, as schematically illustrated on the right. In this case they will
determine the probabilities of statements at all higher level, and partly
constrain the probabilities of statements at deeper levels.

\clearpage

\hrule
Yasser's intro
\hrule
{\footnotesize
Experimental technologies to record the activity of many neurons at the
same time in different species and brain areas are rapidly advancing. These
experimental advancements are paralleled by advances in theoretical and
computational methods for analyzing the data accumulated using the
recording technologies. Such theoretical methods usually take the form of
probabilistic models that try to describe the multi-neuronal activity of
the recorded neurons. With such probabilistic models one aims to address
numerous issues: What correlations are important in describing the
multi-neuronal pattern? How does the pattern of activity covary with
external stimuli or experimental conditions? What dimensionality does the
neural data live in and how is this related to the underlying network
interactions? The probabilistic models can also be used to make predictions
about the structure of the neural code, by studying the properties of the
fitted model, or by generating synthetic data from it.

@@

}
\mynote{Luca: add this: from sampling theory we know that important
  features of the full network may not be visible in a sample because
  smoothed out. But using sampling theory in the inverse direction we can
  infer such full-network features from the sample.}
